Open Science, Open Plant Pathology

### 2020-04-21 analysis/paper/paper.Rmd
Rename import_rrpp() to import_notes() and import 5-year IF

A custom R function, `Reproducibility.in.Plant.Pathology::import_rrpp()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].

@@

import_rrpp() %>%
  tabyl(journal) %>%
  select(-percent) %>%
  flextable() %>%
  set_caption(
    "Table: (\\#tab:journals) Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
  ) %>% 
  autofit()
```

@@

```{r software_avail, echo=FALSE, message=FALSE, warning=FALSE}
import_rrpp() %>%
  tabyl(software_avail) %>%
  select(-percent) %>% 
  rename(`software availability` = software_avail,
         percent = valid_percent) %>% 
  flextable() %>%
  set_caption(
    "Table: (\\#tab:sa) Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available."
  ) %>% 
  autofit()
```

@@

```{r reproducibility_score, echo=FALSE, message=FALSE, warning=FALSE}
import_rrpp() %>% 
  tabyl(reproducibility_score) %>% 
  adorn_pct_formatting() %>% 
  rename(score = reproducibility_score) %>% 
  flextable() %>% 
  set_caption("Table: (\\#tab:reproducibility) Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistcal analysis or other computational code) are freely available for download and use, and raw data are available for download and use.") %>% 
    autofit()

>>>>

A custom R function, `Reproducibility.in.Plant.Pathology::import_notes()`, was written to import the data, format the columns properly and calculate the overall reproducibility score in R [@RCT2020].

@@

import_notes() %>%
  tabyl(journal) %>%
  select(-percent) %>%
  flextable() %>%
  set_caption(
    "Table: (\\#tab:journals) Journal titles selected for inclusion and the number (n) of articles from each journal that were evaluated."
  ) %>% 
  autofit()
```

@@

```{r software_avail, echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>%
  tabyl(software_avail) %>%
  select(-percent) %>% 
  rename(`software availability` = software_avail,
         percent = valid_percent) %>% 
  flextable() %>%
  set_caption(
    "Table: (\\#tab:sa) Article ratings for software availability where '0', not available or not mentioned in publication to '3', preferably open source and freely available."
  ) %>% 
  autofit()
```

@@

```{r reproducibility_score, echo=FALSE, message=FALSE, warning=FALSE}
import_notes() %>% 
  tabyl(reproducibility_score) %>% 
  adorn_pct_formatting() %>% 
  rename(score = reproducibility_score) %>% 
  flextable() %>% 
  set_caption("Table: (\\#tab:reproducibility) Tally of reproducibility scores where 0 is not reproducible and 12 is fully reproducible, _e.g._ all software cited, software used are freely available to anyone, computational methods (statistcal analysis or other computational code) are freely available for download and use, and raw data are available for download and use.") %>% 
    autofit()
